An Automatic Verification Framework for Software Configurations

### 2016-05-08 OSDI/motiv.tex
grammar for entry missing

\para{Example~3: Entry missing errors.} 
Many critical system outages result from the fact that an important
entry was missing in the configuration file. 
We call such a problem as {\em entry missing error}.
In a public misconfiguration dataset~\cite{configdataset},
many MySQL failure reports were caused by
entry missing errors.
Below is a real-world entry missing error example~\cite{yin11anempirical},
when a user wants to use OpenLDAP to enable her directory access
protocol, she needs to use the password policy overlay. This is usually
done through the following entries in the OpenLDAP configuration file:

>>>>

\para{Example~3: Entry missing errors.} 
Many critical system outages result from the fact that an important
entry was missing in the configuration file. 
We call such a problem an {\em entry missing error}.
In a public misconfiguration dataset~\cite{configdataset},
many MySQL failure reports were caused by
missing entry error.
Below is a real-world entry missing error example~\cite{yin11anempirical},
when a user wants to use OpenLDAP to enable her directory access
protocol, she needs to use the password policy overlay. This is usually
done through the following entries in the OpenLDAP configuration file:
